---
title: "UNEMPLOYMENT IN 36 OECD COUNTRIES"
output: 
  flexdashboard::flex_dashboard:
    social: [ "twitter"]
    orientation: rows
    vertical_layout: scroll
    smooth_scroll: true
    html_document:
    theme:
      version: 04
      bg: "#ECD450"
      fg: "#303952"
      primary: "#ECD450"
      navbar-bg: "#303952"
      base_font:
        google: "Lexend Deca"
      code_font:
        google: "Lexend Deca"
    navbar:
      - { title: "DatavizAdventure", href: "https://datavizadventure.com", align: right}
---

```{r setup, include=FALSE}
library(flexdashboard)
library(flexdashboard)
library(tidyverse)
library(readxl)
library(scales)
library(highcharter)

#load data
OECD<-read_csv("Data/OECD Unemployment Rate_Full Data.csv")

#Edition all
OECD_All <- OECD %>%
  filter(Gender == "ALL") %>%
  mutate(Date = lubridate::mdy(Date))

#edition
#edition dates
OECD_dates <- OECD %>%
  filter(Gender == "MEN" | Gender == "WOMEN") %>%
  mutate(Date = lubridate::mdy(Date))

#Rename columns
names(OECD_dates)[names(OECD_dates) == "Unemployement Rate"] <- "Rate"
names(OECD_dates)[names(OECD_dates) == "Country Name"] <- "Country"

#Rename columns for ALL
names(OECD_All)[names(OECD_All) == "Unemployement Rate"] <- "Rate"
names(OECD_All)[names(OECD_All) == "Country Name"] <- "Country"
```

All {data-orientation=rows}
=====================================

Row {data-width=1920}
-----------------------------------------------------------------------

### Australia
    
```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Australia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Australia's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Austria

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Austria")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Austria's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Belgium

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Belgium")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Belgium's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Canada

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Canada")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Canada's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

###
[OECD](https://www.oecd.org) is an international organization that works to build better policies for better lives. Their goal is to shape policies that foster prosperity, equality, opportunity and well-being for all. There are 38 counties that are members of the OECD (from January 2000 to September 2021. There are 2 countries out of the 38 OECD countries that are missing: New Zealand and Switzerland.

In the following dashboard you can explore the **change in unemployment rate across countries between 2000 - 2021** by gender.

Accesed on 30 January 2022.

Challenge: [BACK 2 VIZ BASICS](https://www.thetableaustudentguide.com/vizbasics)

Data Source: [Back 2 Viz Basics - Data.World](https://data.world/back2vizbasics/2022week-2-dates-line-charts)   |   [OECD Unemployment rate](https://data.oecd.org/unemp/unemployment-rate.htm)

Row {data-width=1920}
-----------------------------------------------------------------------

### Chile

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Chile")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Chile's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

   
### Colombia
    
```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Colombia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Colombia's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Costa Rica

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Costa Rica")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Costa Rica's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Czechia

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Czechia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Czechia's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Denmark

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Denmark")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Denmark's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Estonia

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Estonia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Estonia's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```


### Finland
    
```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Finland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Findland's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### France

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="France")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "France's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
Row {data-width=1920}
-----------------------------------------------------------------------

### Germany

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Germany")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Germany's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Greece

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Greece")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Greece's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Hungary

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Hungary")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Hungary's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```


### Iceland
    
```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Iceland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Iceland's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
Row {data-width=1920}
-----------------------------------------------------------------------

### Ireland

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Ireland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Ireland's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Israel

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Israel")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Israel's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Italy

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Italy")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Italy's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Japan

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Japan")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Japan's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------
    
### Korea
    
```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Korea")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Korea's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Latvia

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Latvia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Latvia's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Lithuania

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Lithuania")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Lithuania's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Luxembourg

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Luxembourg")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Luxembourg's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Mexico

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Mexico")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Mexico's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Netherlands
    
```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Netherlands")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Netherlands's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Norway

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Norway")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Norway's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Poland

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Poland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Poland's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Portugal

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Portugal")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Portugal's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Slovakia

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Slovakia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Slovakia's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Slovenia
    
```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Slovenia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Slovenia's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Spain

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Spain")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Spain's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
  
Row {data-width=1920}
-----------------------------------------------------------------------

### Sweden

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Sweden")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Sweden's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Turkey

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="Turkey")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Turkey's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### United Kingdom

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="United Kingdom")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "United Kingdom's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### United States of America

```{r fig.height= 4}

OECD_All%>%
  filter(Country=="United States of America")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "United States of America's rate", color = "#ECD450") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Men {data-orientation=rows}
=====================================

Row {data-width=1920}
-----------------------------------------------------------------------

### Australia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Australia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Australia's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Austria

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Austria")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Austria's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Belgium

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Belgium")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Belgium's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Canada

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Canada")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Canada's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Chile

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Chile")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Chile's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   

### Colombia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Colombia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Colombia's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Costa Rica

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Costa Rica")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Costa Rica's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Czechia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Czechia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Czechia's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Denmark

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Denmark")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Denmark's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Estonia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Estonia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Estonia's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Finland
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Finland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Findland's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### France

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="France")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "France's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
Row {data-width=1920}
-----------------------------------------------------------------------

### Germany

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Germany")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Germany's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Greece

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Greece")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Greece's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Hungary

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Hungary")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Hungary's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Iceland
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Iceland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Iceland's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
Row {data-width=1920}
-----------------------------------------------------------------------

### Ireland

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Ireland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Ireland's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Israel

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Israel")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Israel's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Italy

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Italy")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Italy's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Japan

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Japan")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Japan's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------
    
### Korea
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Korea")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Korea's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Latvia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Latvia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Latvia's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Lithuania

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Lithuania")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Lithuania's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Luxembourg

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Luxembourg")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Luxembourg's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Mexico

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Mexico")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Mexico's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Netherlands
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Netherlands")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Netherlands's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Norway

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Norway")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Norway's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Poland

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Poland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Poland's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Portugal

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Portugal")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Portugal's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Slovakia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Slovakia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Slovakia's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Slovenia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Slovenia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Slovenia's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Spain

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Spain")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Spain's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
  
Row {data-width=1920}
-----------------------------------------------------------------------

### Sweden

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Sweden")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Sweden's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Turkey

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="Turkey")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Turkey's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### United Kingdom

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="United Kingdom")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "United Kingdom's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### United States of America

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="MEN")%>%
  filter(Country=="United States of America")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "United States of America's rate", color = "#3F9DCD") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Women {data-orientation=rows}
=====================================

Row {data-width=1920}
-----------------------------------------------------------------------
    
### Australia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Australia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Australia's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Austria

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Austria")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Austria's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Belgium

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Belgium")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Belgium's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Canada

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Canada")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Canada's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Chile

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Chile")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Chile's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Colombia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Colombia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Colombia's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Costa Rica

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Costa Rica")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Costa Rica's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Czechia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Czechia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Czechia's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Denmark

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Denmark")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Denmark's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Estonia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Estonia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Estonia's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Finland
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Finland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Findland's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### France

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="France")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "France's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Germany

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Germany")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Germany's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Greece

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Greece")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Greece's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Hungary

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Hungary")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Hungary's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Iceland
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Iceland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Iceland's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Ireland

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Ireland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Ireland's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Israel

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Israel")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Israel's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Italy

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Italy")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Italy's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Japan

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Japan")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Japan's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------
    
### Korea
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Korea")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Korea's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Latvia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Latvia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Latvia's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Lithuania

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Lithuania")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Lithuania's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Luxembourg

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Luxembourg")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Luxembourg's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Mexico

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Mexico")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Mexico's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Netherlands
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Netherlands")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Netherlands's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Norway

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Norway")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Norway's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
   
### Poland

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Poland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Poland's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Portugal

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Portugal")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Portugal's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Slovakia

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Slovakia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Slovakia's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Slovenia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Slovenia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Slovenia's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
    
### Spain

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Spain")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Spain's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```
  
Row {data-width=1920}
-----------------------------------------------------------------------

### Sweden

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Sweden")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Sweden's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### Turkey

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="Turkey")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "Turkey's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### United Kingdom

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="United Kingdom")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "United Kingdom's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

### United States of America

```{r fig.height= 4}

OECD_dates%>%
  filter(Gender=="WOMEN")%>%
  filter(Country=="United States of America")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate), name = "United States of America's rate", color = "#F88FE3") %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = FALSE)

```

Men & Women {data-orientation=rows}
=====================================

Row {data-width=1920}
-----------------------------------------------------------------------
    
### Australia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Australia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))
```
    
### Austria

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Austria")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
   
### Belgium

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Belgium")%>%
        hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))


```

### Canada

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Canada")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Chile

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Chile")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Colombia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Colombia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
    
### Costa Rica

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Costa Rica")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
   
### Czechia

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Czechia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Denmark

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Denmark")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Estonia

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Estonia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Finland
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Finland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
    
### France

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="France")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
   
Row {data-width=1920}
-----------------------------------------------------------------------

### Germany

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Germany")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Greece

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Greece")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Hungary

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Hungary")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Iceland
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Iceland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Ireland

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Ireland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
   
### Israel

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Israel")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Italy

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Italy")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Japan

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Japan")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

Row {data-width=1920}
-----------------------------------------------------------------------
    
### Korea
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Korea")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
    
### Latvia

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Latvia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
   
### Lithuania

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Lithuania")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Luxembourg

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Luxembourg")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Mexico

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Mexico")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Netherlands
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Netherlands")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
    
### Norway

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Norway")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
   
### Poland

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Poland")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Portugal

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Portugal")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Slovakia

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Slovakia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Slovenia
    
```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Slovenia")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
    
### Spain

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Spain")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

Row {data-width=1920}
-----------------------------------------------------------------------

### Sweden

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Sweden")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### Turkey

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="Turkey")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### United Kingdom

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="United Kingdom")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```

### United States of America

```{r fig.height= 4}

OECD_dates%>%
  filter(Country=="United States of America")%>%
      hchart(type = "line",
           hcaes(x = Date, y = Rate, group = Gender)) %>%
    hc_yAxis(
      title = list(text = ""),
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#666666"
      )
    ) %>%
    hc_xAxis(title = list(text = ""), labels = list(
      style = list(
        fontFamily = "Roboto",
        fontSize = "10px",
        color = "#333333"
      )
    )) %>%  hc_legend(enabled = TRUE) %>%
  hc_colors(c("#3F9DCD", "#F88FE3"))

```
